---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---

Assignment May_31


```{r}
library(tidyverse)

```


```{r}
as_tibble(iris)
```



```{r}
tibble(
  x = 1:5, 
  y = 1, 
  z = x ^ 2 + y
)
```



```{r}
tb <- tibble(
  `:)` = "smile", 
  ` ` = "space",
  `2000` = "number"
)
tb
```



```{r}
tribble(
  ~x, ~y, ~z,
  #--|--|----
  "a", 2, 3.6,
  "b", 1, 8.5
)
```



```{r}
tibble(
  a = lubridate::now() + runif(1e3) * 86400,
  b = lubridate::today() + runif(1e3) * 30,
  c = 1:1e3,
  d = runif(1e3),
  e = sample(letters, 1e3, replace = TRUE)
)
```


```{r}
nycflights13::flights %>% 
  print(n = 10, width = Inf)
```



```{r}
df <- tibble(
  x = runif(5),
  y = rnorm(5)
)
```



### Exercise 10.5

##### Question 1

You can tell it is a tibble by printing it. If it only prints the first ten lines it is a tibble. It also says it is a tibble when you print it. 

##### Question 2


```{r}
tb

df <- data.frame(abc = 1, xyz = "a")
df
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```


```{r}
df3 <- as_tibble(df)
df3
df3$x
df3[, "xyz"]
df3[, c("abc", "xyz")]
```

In the tibble $x does not work because tibbles need exact names. Not needing exact names can cause some problems.


##### Qestion 3

```{r}
mtcars
vars <- "mpg"

mtcars$mpg

mtcars %>% as_tibble() %>% .[[vars]]
```

##### Question 4

```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)

annoying

# extract variable called 1

annoying$`1`

#scatterplot 
library(ggplot2)

ggplot(annoying, aes(x=`1`,y= `2`))+ geom_point()

# Creating a new column called 3 which is 2 divided by 1

annoying2 <- mutate(annoying, `3`= `2`/`1`)

annoying2

# Renaming the columns to one, two and three.

annoying3 <- transmute(annoying2, "one" = `1`, "two" = `2`, "three" = `3`)
annoying3
```


##### question 5

```{r}
# What does tibble::enframe() do? When might you use it?

?enframe()

enframe(1:3)
enframe(c(a=5, b=7))
```

This converts an atomic vector or a list to a dataframe. 


##### Question 6


```{r}
# What option controls how many additional column names are printed at the footer of a tibble?

#print.tbl_df(annoying)

#print.tbl_df(annoying, n_extra = 5)
```



