---
title: "R Notebook"
output:
  html_document: 
    keep_md: yes
  html_notebook: default
---


### Homework 5

```{r}
library(nycflights13)
library(tidyverse)
library(ggplot2)
```


```{r}
flights
```



```{r}
filter(flights, month == 1, day == 1)

```



```{r}
jan1 <- filter(flights, month == 1, day == 1)

(dec25 <- filter(flights, month == 12, day == 25))
```



```{r}
df <- tibble(x = c(1, NA, 3))
filter(df, x > 1)
filter(df, is.na(x) | x > 1)
```


#### Exercise 5.2.4

##### question 1 
```{r}
#arrival delay 2 or more hours
filter(flights, arr_delay >= 120)

#flew to Houston (IAH or HOU)
filter(flights, dest == "IAH" | dest == "HOU")

#Were operated by United, American, or Delta
filter(flights, carrier == "UA" | carrier == "AA" | carrier == "DL")

#Departed in summer (July, August, and September)
filter(flights, month == 7 | month == 8 | month == 9)

#Arrived more than two hours late, but didn’t leave late
filter(flights, arr_delay > 120 & dep_delay == 0)

#Were delayed by at least an hour, but made up over 30 minutes in flight
filter(flights, dep_delay >= 60 & arr_delay <= 30) 

#Departed between midnight and 6am (inclusive)
filter(flights, dep_time >= 0 & dep_time <= 600)
```


##### question 2

```{r}
?between()

filter(flights, between(flights$dep_time, 0, 600))
```

Between takes values inclusive of two boundary values. ie x >= left & x <= right, yes you can use it to simplify part 7 of question 1.


##### question 3


```{r}
filter(flights, is.na(dep_time))
```

8,255 flights have NA dep_time.

##### question 4

NA....


### Exercise 5.3.1

##### question 2

```{r}
arrange(flights, desc(is.na(flights$dep_time)))
```


##### question 2

```{r}
# most delayed flights
arrange(flights, desc(dep_delay))
# ealiest leaving
arrange(flights, dep_time)


```


##### question 3

```{r}
# fastest flights

arrange(flights, air_time)
```

##### question 4

```{r}
# farthest distance
arrange(flights, distance)

#shortest
arrange(flights, desc(distance))

```


### Exercise 5.4.1


##### question 1

```{r}
# how many ways to select columns dep_time, dep_delay, arr_time, arr_delay

select(flights, dep_time, dep_delay, arr_time, arr_delay)

select(flights, dep_time:arr_delay )

# select(flights, -everything not those)

select(flights, contains("arr"), contains("dep"))
```


##### questions 2

```{r}
select(flights, arr_delay, arr_delay)
```

only comes up once!


##### question 3

```{r}
# what does one_of do

?one_of

vars <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights, one_of(vars) )
```


Allows you to find variables that are contained in a character vector and apply it to select


##### question 4

```{r}
select(flights, contains("TIME"))

?select

#select(flights, ignore.case = FALSE, contains("TIME"))
```


does not worry about case, but this can be changes by, ignore.case = FALSE





### Exercise 5.5.2

##### question 1

```{r}
# new rows with dep_time, sched_dep_time are more convient, minutes past midnight

mutate(flights, departure = dep_time)
```


##### question 2

```{r}
#Compare air_time with arr_time - dep_time. What do you expect to see? What do you see? What do you need to do to fix it?

transmute(flights, in_air = arr_time - dep_time, air_time = air_time)
```


In air is much larger than the actual air time, this might be because dep time and arr time are not in units of minutes, but air_time is. You would have to change the units of the arr time and dep time to minutes


##### question 3

```{r}
# Compare dep_time, sched_dep_time, and dep_delay. How would you expect those three numbers to be related?

transmute(flights, dep_time = dep_time, sched_dep_time = sched_dep_time, dep_delay = dep_delay)
```

The dep delay should equal the difference of dep time and scheduled dep time.


##### question 4

```{r}

#Find the 10 most delayed flights using a ranking function. How do you want to handle ties? Carefully read the documentation for min_rank().

?min_rank()
?ties.method

mutate(flights, most_delayed = desc(min_rank(dep_delay)))
```


Puts every tie to the lowest rank

