---
title: "R Notebook"
output: 
  html_document: 
    keep_md: yes
---

Assignment_ June-14


```{r}
library(tidyverse)
```



```{r}
table1
table2
table3
table4a
table4b
```


### Exercise 12.2.1

##### Question 1

Using prose, describe how the variables and observations are organised in each of the sample tables.

The first data table is a tidy table, as all observations are in rows, the variables are all in columns, and therefor the values are in cells. Table 2 has a column type, which contains two variables, cases and population, and count is the values for each of these two difference variables. Table 3 has a column rate, where it combines the values of cases/population, but it is not split up. Both table 4s have different columns for the years, one containing the values of cases, and the other the values for population.


##### Question 2

```{r}
# table2
table2_tidy <- table2 %>% spread(type, count)
table2_tidy
cases <- table2_tidy %>% select(-population)
cases
population <- table2_tidy %>% select(-cases)
population

table2_tidy <- table2_tidy %>% mutate(rate = (cases$cases/population$population)*10000)
table2_tidy

```

```{r}
# table 4s
table4a
table4b

cases2 <- table4a %>%  gather(`1999`, `2000`, key = "year", value = "cases")
cases2
population2 <- table4b %>%  gather(`1999`, `2000`, key = "year", value = "population")
population2

table4_tidy <- population2 %>% mutate(rate = (cases2$cases/population2$population)*10000) 
table4_tidy
#table4_tidy <- mutate(table4_tidy, cases2$cases)
#table4_tidy

```


##### Question 3


```{r}
library(ggplot2)
ggplot(table2_tidy, aes(year, cases)) + 
  geom_line(aes(group = country), colour = "grey50") + 
  geom_point(aes(colour = country))
```

You gotta make it tidy.




### Exercise 12.3.3


##### Quesiton 1

Why are gather() and spread() not perfectly symmetrical?

```{r}
stocks <- tibble(
  year   = c(2015, 2015, 2016, 2016),
  half  = c(   1,    2,     1,    2),
  return = c(1.88, 0.59, 0.92, 0.17))

stocks
stocks %>% 
  spread(year, return) %>% 
  gather("year", "return", `2015`:`2016`)
```

Spread and gather are not symetrical, because when you spread you are telling it to take a column, first argument, and spread it out by the variables in that column. The second argument is values that will go into the cells of the new columns, formed from the variables from the first argument. When using gather, you first are naming the new column, you are creating to combine columns/variables, then you have to name the new coulmn of values that are spread throughtout the columns you are combining. And last here you are putting the columns you are combining. Spread only requires 2 arguments, and gather requires 3, this is because you in gather you have to tell it which columns you are putting into a new column, while spread will name the new columns based on the values within the column you are spreading. 



##### Question 2

```{r}
# Why does this code fail?

#table4a %>% gather(1999, 2000, key = "year", value = "cases")

table4a

table4a %>% gather(`1999`, `2000`, key = "year", value = "cases")
```


##### Question 3

Why does spreading this tibble fail? How could you add a new column to fix the problem?

```{r}
people <- tribble(
  ~name,             ~key,    ~value,
  #-----------------|--------|------
  "Phillip Woods",   "age",       45,
  "Phillip Woods",   "height",   186,
  "Phillip Woods",   "age",       50,
  "Jessica Cordero", "age",       37,
  "Jessica Cordero", "height",   156)

people

# people_spread_out <- people %>% spread(key, value)


```

Can't spread because you have 2 ages for the name Philip Woods. 



##### Question 4


```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)

preg

gather(preg, sex, count, male, female) %>% mutate(pregnant = pregnant == "yes", female = sex == "female") %>% select(-sex)
```




### Exercise 12.4.3


##### Question 1

```{r}
# What do the extra and fill arguments do in separate()? Experiment with the various options for the following two toy datasets?

?separate()

tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "drop")

tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "merge")


tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill = "right")

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill = "left")

```

Extra gives you options for what to do when there are too many pieces, if sep is a character vector. The options are to warn, drop, or merge. Fill is the opposite, where you have options when there are not enough pieces if sep is a character vector. These options are warn, right, and left.


##### Question 2

Both unite() and separate() have a remove argument. What does it do? Why would you set it to FALSE?


```{r}
?unite()
?separate()
```


The remove argument removes the input columns from the output data frame. I'd imagine you would set it to FALSE, if for some reason you still wanted the original column you are seperating, as well as the new columns.


##### Question 3

```{r}
# Compare and contrast separate() and extract(). Why are there three variations of separation (by position, by separator, and with groups), but only one unite?

?separate()
?extract()
```

Seperate, turns 1 column into multiple, while extract turns multiple columns into 1.  










