---
title: "R Notebook"
output: 
  html_document: 
    keep_md: yes
---

Assignment June 7 


```{r}
library(tidyverse)
```



```{r}
read_csv("a,b,c
1,2,3
4,5,6")
#> # A tibble: 2 × 3
#>       a     b     c
#>   <int> <int> <int>
#> 1     1     2     3
#> 2     4     5     6
```



```{r}
read_csv("The first line of metadata
  The second line of metadata
  x,y,z
  1,2,3", skip = 2)
#> # A tibble: 1 × 3
#>       x     y     z
#>   <int> <int> <int>
#> 1     1     2     3

read_csv("# A comment I want to skip
  x,y,z
  1,2,3", comment = "#")
#> # A tibble: 1 × 3
#>       x     y     z
#>   <int> <int> <int>
#> 1     1     2     3
```


```{r}
read_csv("1,2,3\n4,5,6", col_names = FALSE)
#> # A tibble: 2 × 3
#>      X1    X2    X3
#>   <int> <int> <int>
#> 1     1     2     3
#> 2     4     5     6
```


### Exercise 11.2.2



##### question 1

What function would you use to read a file where fields were separated with
“|”?

```{r}
?read_delim()
```


You could use read_delim, and specify the delim as |.


##### question 2


```{r}
# Apart from file, skip, and comment, what other arguments do read_csv() and read_tsv() have in common?

?read_csv
?read_tsv
```


They also have col_names, col_types, locale, na = , quote, trim_ws, n_max, progress bar, and guess_max.


##### Question 3

```{r}
#What are the most important arguments to read_fwf()?

?read_fwf
```

Col_positions, which are created by fwf_widths or fwf_positions


##### question 4

```{r}
#Sometimes strings in a CSV file contain commas. To prevent them from causing problems they need to be surrounded by a quoting character, like " or '. By convention, read_csv() assumes that the quoting character will be ", and if you want to change it you’ll need to use read_delim() instead. What arguments do you need to specify to read the following text into a data frame?


"x,y\n1,'a,b'"

?read_delim
read_csv("x,y\n1,'a,b'", quote = "'")
```


##### Question 5

```{r}
# Identify what is wrong with each of the following inline CSV files. What happens when you run the code?

#read_csv("a,b\n1,2,3\n4,5,6")

read_csv("a,b,c\n1,2,3\n4,5,6")

read_csv("a,b,c\n1,2\n1,2,3,4")
read_csv("a,b,c,d\n1,2\n1,2,3,4")

#read_csv("a,b\n\"1")
#read_csv("a,b\n\"1"", quote = "" )
#read_csv("a,b\n1,2\na,b")
#read_csv("a;b\n1;3")

```



### Exercise 11.3.5


##### Question 1

What are the most important arguments to locale()?

```{r}
?locale()
```

The decimal_mark argument is the most important. 


##### Question 2

```{r}
# What happens if you try and set decimal_mark and grouping_mark to the same character? What happens to the default value of grouping_mark when you set decimal_mark to “,”? What happens to the default value of decimal_mark when you set the grouping_mark to “.”?

#locale(decimal_mark = ".", grouping_mark = ".")
# does not work
locale(decimal_mark = ",")

# it swapped the default

locale(grouping_mark = ".")
# switches the default
```



##### Question 3


```{r}
#I didn’t discuss the date_format and time_format options to locale(). What do they do? Construct an example that shows when they might be useful

# they change the format of how you can inout the date or time.
?date_format
locale(date_format = "%m-%d-%Y")
?parse_date()
parse_date("12-27-1991", locale = locale(date_format = "%m-%d-%Y"))

```


##### Question 4

```{r}
# If you live outside the US, create a new locale object that encapsulates the settings for the types of file you read most commonly.

# Germany does day month year, months in numbers 
locale(date_format = "%d-%m-%Y")
# or change locale to German and use month names
locale("de", date_format = "%d-%b-%Y")
```



##### Question 5

What’s the difference between read_csv() and read_csv2()?

csv is comma deliminated and csv2 is semi-colon deliminated



##### Question 6

What are the most common encodings used in Europe? What are the most common encodings used in Asia? Do some googling to find out.


##### Question 7

Generate the correct format string to parse each of the following dates and times:

```{r}
d1 <- "January 1, 2010"
d2 <- "2015-Mar-07"
d3 <- "06-Jun-2017"
d4 <- c("August 19 (2015)", "July 1 (2015)")
d5 <- "12/30/14" # Dec 30, 2014
t1 <- "1705"
t2 <- "11:15:10.12 PM"


#d1
parse_date(d1, locale = locale(date_format = "%B %d, %Y"))
#d2
parse_date(d2, locale = locale(date_format = "%Y-%b-%d"))
#d3
parse_date(d3, locale = locale(date_format = "%d-%b-%Y"))
#d4
parse_date(d4, locale = locale(date_format = "%B %d (%Y)"))
#d5
parse_date(d5, locale = locale(date_format = "%m/%d/%y"))
#t1
parse_time(t1, locale = locale(time_format = "%H%M"))
#t2
parse_time(t2, locale = locale(time_format = "%H:%M:%OS %p"))
```







